### 2020-06-28 README.Rmd

```{r intallation2, eval=FALSE, include=TRUE}
# the repo at the moment is private so you need to be authorized 
# don't share the token
library(devtools)

devtools::install_github("c1au6i0/covid19census_dev", auth_token = "8ca5cd2bb556a45f1ffeb2e9b44c90d4fbef6cf2", ref = "dev")
```

>>>>

```{r intallation2, eval=FALSE, include=TRUE}
library(devtools)

devtools::install_github("c1au6i0/covid19census")
```
